### 2020-06-24 response2.tex
Suggestions for response letter (including some that need to move to MS).

\usepackage{natbib}
\bibliographystyle{chicago}

@@

``Instead, we model the estimate of \Ro (as well as the associated generation-interval parameters, $\bar G$, and $\kappa$) from each study with probability distributions that account for the uncertainty in the estimates;
this allows us to re-estimate the corresponding distributions of the exponential growth rates $r$.
We then use a Bayesian multi-level model to calculate the average (pooled estimates) of three key quantities ($r$, $\bar G$, and $\kappa$).
The resulting pooled estimates ($\mu_r$, $\mu_G$, and $\mu_\kappa$) are used to calculate the pooled estimate of the basic reproduction number, \Rpool.
Calculating \Rpool based on the pooled estimates allows us to average appropriately across the uncertainties present in modeling approaches and in their underlying assumptions.''

@@

We tried to be as careful as possible in the uses of confidence and credible intervals.
When we refer to based estimates, however, we still use credible intervals because the base estimates are our approximations of the reported estimates (taken from each study); we have tried to make this distinction clear in the text.

@@

``Although this approach assumes that all studies are equally weighted, the overall pooled estimate will still be weighted by the certainty of the reported estimates (e.g., $r_i$ will be sampled from a narrow distribution and therefore have stronger influence on $\mu_r$ if the reported confidence/credible interval on $r_i$ is narrow).''

@@

``Emergence of a new strain (or a clade) with different transmissibility can also affect disease dynamics as well as inference, although it is less likely to be of a concern in the beginning of an epidemic.''

\pagebreak

\bibliography{ncov_abbr.bib}

>>>>

@@

``Instead, we model the estimate of \Ro (as well as the associated generation-interval parameters, $\bar G$, and $\kappa$) from each study with probability distributions that account for the uncertainty in the estimates;
this allows us to re-estimate the corresponding distributions of the exponential growth rates $r$.
We then use a Bayesian multi-level model to estimate the three  key quantities ($r$, $\bar G$, and $\kappa$).
The resulting pooled estimates ($\mu_r$, $\mu_G$, and $\mu_\kappa$) are used to calculate the pooled estimate of the basic reproduction number, \Rpool.
Using pooled estimates allows us to average appropriately across the uncertainties present in modeling approaches and in their underlying assumptions.''

@@

We tried to be as careful as possible in the uses of confidence and credible intervals.
We still describe our base estimates with credible intervals because the base estimates are our Bayesian approximations based on the reported estimates taken from each study; we have tried to make this distinction clear in the text.

@@

``Although this approach nominally treats all studies are equally weighted, the overall pooled estimate will still be weighted by the certainty of the reported estimates (e.g., $r_i$ will be sampled from a narrow distribution and therefore have stronger influence on $\mu_r$ if the reported confidence/credible interval on $r_i$ is narrow).''

@@

``Emergence of a new strain (or a clade) with different transmissibility could also affect disease dynamics, and complicate inference; this study does not address this possibility.''
